Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-07-15 analysis/report/effectiveness_report.Rmd
update rmd

## Unadjusted survival curves

```{r, curves, echo=FALSE, message=FALSE, out.width='90%'}

print_plots <- function(outcome, outcome_descr){
  km_image <- here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.png"))
  calendar_image <- here("output", outcome, "calendar", glue("forest_plot_cox.png"))
  timesincevax_image <- here("output", outcome, "timesincevax", glue("forest_plot_cox.png"))

  km_plot <- read_rds(here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.rds")))
  calendar_plot <- read_rds(here("output", outcome, "calendar", glue("forest_plot_cox.rds")))
  timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("forest_plot_cox.rds")))

@@

  effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1, guides='collect')

  wrap_plot(
    km_plot+theme(legend.position = c(0.1,0.1), legend.justification = c(0,0)), 
    effects_plot, 
    ncol=1,
  ) + 
  plot_annotation(title = '{outcome_descr}')

@@

print_plots("test", "SARS-CoV-2 test")
print_plots("postest", "SARS-CoV-2 positive test")
print_plots("emergency", "A&E attendances")
print_plots("covidadmitted", "COVID-19 hospital admission")
print_plots("covidcc", "COVID-19 critical care admission")

>>>>

## Comparative effectiveness

The plots below show unadjusted Kaplan-Meier curves, and the *ChAdOx1* versus *BNT162b2* hazard ratios for each model.

```{r, curves, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%'}

print_plots <- function(outcome, outcome_descr){
  km_image <- here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.png"))
  calendar_image <- here("output", outcome, "calendar", glue("effect_plot_cox.png"))
  timesincevax_image <- here("output", outcome, "timesincevax", glue("effect_plot_cox.png"))

  km_plot <- read_rds(here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.rds")))
  km_plot <- km_plot + theme(legend.position = c(0.1,0.1), legend.justification = c(0,0))

  calendar_plot <- read_rds(here("output", outcome, "calendar", glue("effect_plot_cox.rds"))) + 
    labs(title=NULL)+
    coord_cartesian(ylim=c(0.25,4))+
    theme(text = element_text(size=10))

  timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("effect_plot_cox.rds"))) + 
    labs(title=NULL)+
    coord_cartesian(ylim=c(0.25,4))+
    theme(text = element_text(size=10))

@@

  effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1)#, guides='collect')

  wrap_plots(
   km_plot,
   effects_plot,
   ncol=1
  ) +
  plot_annotation(title = outcome_descr)

@@

print_plots("test", "SARS-CoV-2 test")
print_plots("postest", "SARS-CoV-2 positive test")
print_plots("emergency", "A&E attendance")
print_plots("covidadmitted", "COVID-19 hospital admission")
#print_plots("covidcc", "COVID-19 critical care admission")
